Optimizing Abstract Abstract Machines

### 2012-11-14 paper/paper.tex
Played around with the intro

\newcommand{\naive}{na\"ive}
\newcommand{\naively}{ na\"ively}
\newcommand{\Naive}{Na\"ive}
\newcommand{\Naively}{Na\"ively}
% \usepackage{xltxtra}
% \setmonofont[Scale=MatchLowercase]{DejaVu Sans Mono}
%
\input{preamble}

@@

The \emph{abstracting abstract machines} (AAM)
approach~\cite{dvanhorn:VanHorn2011Abstracting,dvanhorn:VanHorn2012Systematic}
to deriving program analyses provides a straightforward way of
transforming a programming language semantics in the form of an
abstract machine, into a family of abstract interpreters parameterized
over policies for regulating the analytic precision of the control,
environment, store, and base value domains.  By taking a
machine-oriented view of computation, it becomes possible to design,
verify, and implement program analyzers for realistic language
features typically considered difficult to model.  The approach was
originally applied to features such as higher-order functions,
stack inspection, exceptions, laziness, first-class continuations, and
garbage collection.  It has since been used to verify actor-
\cite{local:DOsualdo:12A} and
thread-based~\cite{dvanhorn:Might2011Family} parallelism and
behavioral contracts~\cite{dvanhorn:TobinHochstadt2012Higherorder}; it
has been used to model Coq~\cite{local:harvard},
Dalvik~\cite{local:dalvik}, Erlang~\cite{local:DOsualdo:12B},
JavaScript~\cite{local:DBLP:journals/corr/abs-1109-4467}, and
Racket~\cite{dvanhorn:TobinHochstadt2012Higherorder}.

>>>>

\newcommand{\naive}{naive}
\newcommand{\naively}{naively}
\newcommand{\Naive}{Naive}
\newcommand{\Naively}{Naively}
% \usepackage{xltxtra}
% \setmonofont[Scale=MatchLowercase]{DejaVu Sans Mono}
%
\input{preamble}

@@

The \emph{abstracting abstract machines} (AAM)
approach~\cite{dvanhorn:VanHorn2011Abstracting,dvanhorn:VanHorn2012Systematic}
to deriving program analyses provides a systematic way of transforming a
programming language semantics in the form of an abstract machine into a family
of abstract interpreters.
%
The approach parameterizes these families with policies for regulating analytic
precision.
%
While flexible and robust, the AAM approach unfortunately yields analyzers with
poor performance relative to hand-optimized analyzers.
%
Our work takes aim squarely at this ``efficiency gap,'' and narrows it in an
equally systematic way.

%
% Specifically, these policies tune precision for control,
% the environment, the store, and base value domains.

By taking a
machine-oriented view of computation, AAM makes it possible to design,
verify, and implement program analyzers for realistic language
features typically considered difficult to model.  The approach was
originally applied to features such as higher-order functions,
stack inspection, exceptions, laziness, first-class continuations, and
garbage collection.  It has since been used to verify actor-
\cite{local:DOsualdo:12A} and
thread-based~\cite{dvanhorn:Might2011Family} parallelism and
behavioral contracts~\cite{dvanhorn:TobinHochstadt2012Higherorder}; it
has been used to model Coq~\cite{local:harvard},
Dalvik~\cite{local:dalvik}, Erlang~\cite{local:DOsualdo:12B},
JavaScript~\cite{local:DBLP:journals/corr/abs-1109-4467}, and
Racket~\cite{dvanhorn:TobinHochstadt2012Higherorder}.
